---
title: "Exercise #X"
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
author: "Name (Martrikelnummer), Name (Martrikelnummer), ..."
date: "`r Sys.Date()`"
---


## Exercise 1: Initializing git

### d)

Strengths of git:
  - ideal for collaboration with other people on a (software) project
  - pulling/fetching/merging/rebasing is very fast

Weaknesses of git:
  - large binary files (e.g. for game devellopment) are not handled very well by git (but there exists the extension git LFS to fix this)
  - git can be quite complicated for a new user

## Exercise 3: Baby-Names in Munich (4.5 Points)

### b)

```{r message=FALSE, warning=FALSE}
# load data
library(readr)
first_names_2021 <- read_csv("vornamen_2021.csv")
first_names_2022 <- read_csv("open_data_portal_2022.csv")
head(first_names_2021)
```


```{r message=FALSE, warning=FALSE}
class(first_names_2021$Anzahl)
class(first_names_2022$Anzahl)
# The colum "Anzahl" is has the type character.
# it looks like for everyname which has 4 or less ocurrences the table doesn't 
# specify a exact number but instead "4 oder weniger". Because it is ok that some
# of the counts are inaccurate we just convert "4 oder weniger" to a 4 and 
# convert the colum to a numeric.
first_names_2021$Anzahl <- gsub("4 oder weniger", "4", first_names_2021$Anzahl)
first_names_2022$Anzahl <- gsub("4 oder weniger", "4", first_names_2022$Anzahl)
first_names_2021$Anzahl <- as.numeric(first_names_2021$Anzahl)
first_names_2022$Anzahl <- as.numeric(first_names_2022$Anzahl)
```

c)  Calculate the total number of babies born in Munich in 2022
    and 2021. Which year had the bigger baby-boom?

d)  Add a new column `year` to both datasets which holds the correct
    year for each.

e)  Combine both datasets into one using `bind_rows()`.

f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.

## Exercise 4: Chat GPT + apply (3 points)

For this task: Specifically use ChatGPT to solve the task and submit
your prompts in addition to the solution

a)  The code below does not work because the wrong apply function has
    been used. Find out which apply function would be correct and why it
    did not work. Correct the code. Also calculate the rowwise means.

###Create a sample data frame

tax_data \<- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
3400) )

###Calculate column-wise means

column_means \<- lapply(tax_data\[, -1\], 2, mean)

column_means

b)  Using ChatGPT try to understand what the rapply() function does.
    Create an easy example with mock data where the function is used and
    explain it in your words.

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
